STAT0017 ICA2

### 2019-04-29 STAT0017_ICA2/17052480.Rmd
final test

loglike_fun <- function(x1, x2, mu1, mu2, sigma1, sigma2, rho) 
{         
  par1<-par[1]
  par2<-par[2]

  n=length(u1)
  vec=matrix(data=0,nrow=n,ncol=1)

  vec=dnorm(u1, mean = par1, sd = par2)

  sumlik=-sum(dmvnorm(cbind(x1,x2), c(0,0), matrix(c(1, rho, rho, 1), ncol=2), log=T));

  # Output
  cat("Normal log-likelihood ->",sprintf("%4.4f",- sumlik),"\n")

@@

```{r}
fit <- BiCopEst(u1,u2,family=1,method="mle",se=TRUE) 
BiCopPDF(u1, u2, family=1,par = fit$par,par2 = fit$par2) 
#the resulting estimate with the parameter value estimated using function BiCopEst.
```

#(d)

>>>>

loglike_fun <- function(x1, x2, mu1, mu2, sigma1, sigma2, rho) 
{         
  par1<-par[1]
  par2<-par[2]
  rho <-par[3]
  n=length(u1)
  sumlik=-sum(dmvnorm(cbind(u[,1],u[,2]), c(par1,par2), matrix(c(1, rho, rho, 1), ncol=2), log=T))

  # Output
  cat("log-likelihood ->",sprintf("%4.4f",- sumlik),"\n")

@@

```{r}
library("CDVine")
fit <- BiCopEst(u[,1],u[,2],family=1,method="mle",se=TRUE)
#BiCopPDF(u1, u2, family=1,par = fit$par,par2 = fit$par2) 
#the resulting estimate with the parameter value estimated using function BiCopEst.
```
